wgcna

### 2019-08-22 analysis/08_wgcna.Rmd
now with subsets

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = FALSE, fig.path = '../figures/wgcna/')

@@

## WGCNA

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.path = '../figures/wgcna/')

@@

## All characterization data

This first image was made using [`08_WGCNA_1.R`](https://github.com/macmanes-lab/DoveParentsRNAseq/blob/master/analysis/08_WGCNA_1.R), which was modified from the [first in a series of WGCNA tutorial](https://horvath.genetics.ucla.edu/html/CoexpressionNetwork/Rpackages/WGCNA/Tutorials/Consensus-DataInput.R). The first tutorial focuses on data input, cleaning and pre-processing; outlier removal; clustering of samples by their Euclidean distance; a comparison of sample cluster to sample meta data.

@@

## hypothalas

```{r wgcna-hyp, message=FALSE, warning=FALSE, cache=TRUE}
source("08_WGCNA_1_params.R")
subsetWGCNA("hypothalamus")

## pituitary

```{r wgcna-pit, message=FALSE, warning=FALSE, cache=TRUE}

subsetWGCNA("pituitary")
```

## gonads

```{r wgcna-gon, message=FALSE, warning=FALSE, cache=TRUE}
subsetWGCNA("gonad")
```
